Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-10-01 completeness.tex
tables are updated.

\begin{table*}%[t]
    \centering
    \caption{Year thresholds and magnitude completeness for the seismic zones within the region of interest in this study. Year of completeness is provided for magnitude ranges between 3 and 7, with $\mathrm{\Delta}M = 1$. The completeness magnitude is provided for the sub-catalogs for three year intervals.}
    \begin{tabular}{lccccrcccccc}
        \cline{2-12}                                                                                  			\\[-1.6ex]
                        & \multicolumn{5}{c}{Year for $M_w$ ranges} 
                                                            & & \multicolumn{3}{c}{$M_c$ for sub-catalogs} & &$M_c$\\
        \cline{2-6} \cline{8-10}                                                                      			\\[-1.6ex]
                        & 3--4 & 4--5 & 5--6 & 6--7 & \multicolumn{1}{c}{$>7$} 
                                                            & & 1800--1899 & 1900--1999 & 2000--2015  & & Whole	\\[0.6ex]
        \hline                                                                                        			\\[-1.6ex]
        Azerbaijan      & 1961 & 1961 & 1900 & 1581 & 1042  & &     6.0    &     5.0    &     4.2     & &  4.2 	\\
        Alborz          & 2005 & 1961 & 1900 & 1664 &--401  & &     6.2    &     5.0    &     3.5     & &  4.3 	\\
        Kopeh Dagh      & 2005 & 1950 & 1924 & 1673 &    9  & &     6.1    &     5.0    &     4.0     & &  4.9 	\\
        Zagros          & 2005 & 1961 & 1950 & 1853 & 1439  & &     5.3    &     4.8    &     3.9     & &  4.8 	\\
        Central-East    & 2005 & 1961 & 1900 & 1837 &  762  & &     5.5    &     4.8    &     4.0     & &  4.8 	\\
        Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401  & &     6.1    &     4.8    &     3.8     & &  4.8 	\\[0.5ex]
        \hline 
    \end{tabular}
    \label{tab:completeness} 
\end{table*}

>>>>

\begin{table*}%[t]
    \centering
    \caption{Year thresholds and magnitude completeness for the seismic zones within the region of interest in this study. Year of completeness is provided for magnitude ranges between 3 and 7, with $\mathrm{\Delta}M = 1$. The completeness magnitude is provided for the sub-catalogs for three year intervals.}
    \begin{tabular}{lccccrcccccc}
        \cline{2-12}                                                                                  			\\[-1.6ex]
                        & \multicolumn{5}{c}{Year for $M_w$ ranges} 
                                                            & & \multicolumn{3}{c}{$M_c$ for sub-catalogs} & & \\
        \cline{2-6} \cline{8-10}                                                                      			\\[-1.6ex]
                        & 3--4 & 4--5 & 5--6 & 6--7 & \multicolumn{1}{c}{$>7$} 
                                                            & & 1800--1899 & 1900--1999 & 2000--2015  	\\[0.6ex]
        \hline                                                                                        			\\[-1.6ex]
        Azerbaijan      & 2005 & 1961 & 1900 & 1581 & 1042  & &     5.8    &    4.9    &     3.6    \\
        Alborz          & 2005 & 1961 & 1900 & 1664 &--401  & &     6.2    &     5.0    &     3    \\
        Kopeh Dagh      & 2005 & 1950 & 1924 & 1673 &    9  & &     6.1    &     5.0    &     3.9    \\
        Zagros          & 2005 & 1961 & 1950 & 1853 & 1439  & &     5.3    &     4.8    &     3.9     \\
        Central-East    & 2005 & 1961 & 1900 & 1837 &  762  & &     5.5    &     4.8    &     3.6   \\
        Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401  & &     6.1    &     4.9    &     3.9   \\[0.5ex]
        \hline 
    \end{tabular}
    \label{tab:completeness} 
\end{table*}

### 2016-10-01 parameters.tex
tables are updated.

We obtain $b$ and $M_{\max}$ for two different models. In the first model we obtain these parameters independently for each one of the five seismic zones influencing the hazard in northern Iran. We call this the \textit{R Model}. In it we obtain distinct values of $b$ and $M_{\max}$ for the main northern seismic zones of Azerbaijan, Alborz, and Kopeh Dagh, as well as for the Zagros and Central-East seismic zones contributing to our region of interest (see Fig.~\ref{fig:iran} for reference). In the second model we consider the whole study area as a uniform seismic zone. We call it the \textit{U Model}. Admittedly, this assumption is somewhat unrealistic if considered from the point of view that different seismic zones \myrevision{may have different values of $b$ and $M_{max}$}. However, as it will be seen in the Results and Analysis section, computing results for this uniform model was useful because it allowed us to find a combination model computation of hazard in the region of interest as a means to \myrevision{account for} epistemic uncertainty. Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained with HA3 for the five seismic zones in the R model and the corresponding ones for the U model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$; and Fig.~\ref{fig:annualp} shows the annual probability of exceedance as a function of earthquake magnitude.

\begin{table}%[t]
    \centering
    \caption{Seismicity parameters $b$ and $M_{\max}$ computed for the seismic zones in our region of interest and the reference uniform seismicity model along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$.}
    \begin{tabular}{@{\hspace{0.2ex}}lccc@{\hspace{0.2ex}}}
        \cline{2-4}                                                                         \\[-1.6ex]
                        & $b$-value         & $M_{\max}$        & $M_{\max}^{\mathrm{obs}}$ \\[0.6ex]
        \hline                                                                              \\[-1.6ex]
        Azerbaijan      & 1.16 $\pm$ 0.03   & 7.80 $\pm$ 0.38   & 7.7                       \\
        Alborz          & 1.00 $\pm$ 0.03   & 7.80 $\pm$ 0.52   & 7.8                       \\
        Kopeh Dagh      & 0.92 $\pm$ 0.03   & 7.73 $\pm$ 0.28   & 7.6                       \\
        Zagros          & 1.02 $\pm$ 0.02   & 7.48 $\pm$ 0.26   & 7.4                       \\
        Central-East    & 1.01 $\pm$ 0.03   & 7.79 $\pm$ 0.31   & 7.6                       \\
        Uniform Model   & 0.95 $\pm$ 0.01   & 7.84 $\pm$ 0.27   & 7.8                       \\[0.5ex]
        \hline 
    \end{tabular}
    \label{tab:params} 
\end{table}

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-07} 
    \caption{Annual probability of exceedance as a function of earthquake magnitude for the seismic zones in the region of interest. The three curves in red correspond to those seismic zones completely considered within the study area, whereas the ones in blue are the two additional contributing zones from the rest of the country. The last curve in green corresponds to the complete region of interest, here referred to as the uniform model. The shaded range indicates the models' $\pm 1$ standard deviation.}
    \label{fig:annualp}
\end{figure*}

>>>>

We obtain $b$ and $M_{\max}$ for two different models. In the first model we obtain these parameters independently for each one of the five seismic zones influencing the hazard in northern Iran. We call this the \textit{R Model}. In it we obtain distinct values of $b$ and $M_{\max}$ for the main northern seismic zones of Azerbaijan, Alborz, and Kopeh Dagh, as well as for the Zagros and Central-East seismic zones contributing to our region of interest (see Fig.~\ref{fig:iran} for reference). In the second model we consider the whole study area as a uniform seismic zone. We call it the \textit{U Model}. Admittedly, this assumption is somewhat unrealistic if considered from the point of view that different seismic zones \myrevision{may have different values of $b$ and $M_{max}$}. However, as it will be seen in the Results and Analysis section, computing results for this uniform model was useful because it allowed us to find a combination model computation of hazard in the region of interest as a means to \myrevision{account for} epistemic uncertainty. Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained with HA3 for the five seismic zones in the R model and the corresponding ones for the U model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$; and Fig.~\ref{fig:annualp} shows the annual probability of exceedance as a function of earthquake magnitude.
\myrevision{
\begin{table}%[t]
    \centering
    \caption{Seismicity parameters $b$ and $M_{\max}$ computed for the seismic zones in our region of interest and the reference uniform seismicity model along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$.}
    \begin{tabular}{@{\hspace{0.2ex}}lccc@{\hspace{0.2ex}}}
        \cline{2-4}                                                                         \\[-1.6ex]
                        & $b$-value         & $M_{\max}$        & $M_{\max}^{\mathrm{obs}}$ \\[0.6ex]
        \hline                                                                              \\[-1.6ex]
        Azerbaijan      & 1.15 $\pm$ 0.03   & 7.80 $\pm$ 0.50   & 7.7                       \\
        Alborz          & 0.97 $\pm$ 0.02   & 7.82 $\pm$ 0.52   & 7.8                       \\
        Kopeh Dagh      & 0.93 $\pm$ 0.03   & 7.74 $\pm$ 0.29   & 7.6                       \\
        Zagros          & 1.05 $\pm$ 0.02   & 7.48 $\pm$ 0.26   & 7.4                       \\
        Central-East    & 0.99 $\pm$ 0.02   & 7.80 $\pm$ 0.37   & 7.6                       \\
        Uniform Model   & 0.98 $\pm$ 0.01   & 7.80 $\pm$ 0.28   & 7.8                       \\[0.5ex]
        \hline 
    \end{tabular}
    \label{tab:params} 
\end{table}
}
\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-07} 
    \caption{Annual probability of exceedance as a function of earthquake magnitude for the seismic zones in the region of interest. The three curves in red correspond to those seismic zones completely considered within the study area, whereas the ones in blue are the two additional contributing zones from the rest of the country. The last curve in green corresponds to the complete region of interest, here referred to as the uniform model. The shaded range indicates the models' $\pm 1$ standard deviation.}
    \label{fig:annualp}
\end{figure*}
